Machine Learning is considered the main sub-area of AI(Artificial Intelligence), since it has as main goal to make a 
computer learn alone how to perform a given task, without the steps of this task being previously programmed
and when receives new data, the way how it performs this task will be optimized. 
It has a division into categories, which is given by the organization of the data used to learning, the categories are
supervised, unsupervised, semi-supervised and reinforcement learning. 


This area encourages the advancement and development of new methods, algorithms and technologies. Both the academic environment 
and the corporate environment understand the possibilities of machine learning, however the corporate environment is 
the main motivator of the advances, because it is possible that when applying machine learning to market data a 
great competitive advantage. In addition to large companies that offer services to abstract the complexity of a 
machine project learning and facilitate its application.


It is a qualitative research using the bibliographical procedure by referring articles, books and posts on the internet
about the subject. It can be concluded from the reading of this paper that there are several
methods to apply machine learning and the choice of what best suits the context is very important because it depends on the 
organization of the data used. Besides to present the main tools and technologies of the area.

% Separe as palavras-chave por ponto
\keywords{AI;Machine Learning;}
